2nd_draft

### 2020-03-19 src/2nd_draft.Rmd
final assign
one more assign

```{r, warning=F, message=F, echo=FALSE}
## data setup
## Aggregated Data
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))[,-1]
#assessment_2020 <- read.csv(here("data","assessment_2020.csv"))[,-1]
#assessment_2020.full <- read_excel(here("data/Assessment", "2020 Only.xlsx"))
```

@@

```{r fit, echo=FALSE}
## choose transformed model
linear_1<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+AvgTotalAssessmentValue,data=assessment_transform)

@@

## References

@@

## Appendix

>>>>

```{r, warning=F, message=F, echo=FALSE}
## data setup
## Aggregated Data
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))[,-1]
assessment_2020 <- read.csv(here("data","assessment_2020.csv"))[,-1]
assessment_2020.full <- read_excel(here("data/Assessment", "2020 Only.xlsx"))
```

@@

##_______________________________________
##TODO: make prediction work for 2020 data (Yuetong)
##(it's missing AvgTotalAssessmentValue, looks like we need to calculate them)
```{r fit, echo=FALSE}
## choose transformed model
linear_1<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+AvgTotalAssessmentValue,data=assessment_transform)

@@

\pagebreak
## References

@@

##——————————————————————————
##TODO: more styling (Yuting)
##___________________________
## Appendix

##__________________________
## TODO: add one more section: (Yuetong)
## Include the code relevant to summarizing and aggregating the data from the client, which produces in the dataframe used for analysis.
##__________________________
